Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/paper.tex
#29 v0.9.5

Having discussed issues with internal validity now, I will briefly talk about external validity. For this purpose it is helpful to first put the goal of my paper into context. 
\cite{cantoni2021}

I doubt that we can learn anything about present conflicts or present growth rates from my results.

In terms of \cite{levine2021, levine2022}'s model of state systems, most international conflict nowadays is defined by the presence of multiple extremely strong outsiders who act to keep the balance of power in the status quo.

@@

>>>>

Having discussed issues with internal validity now, I will briefly talk about external validity. The hypothesis I test is a prediction of the theory of conflict-driven evolution. While the theory itself can be applied widely --- \cite{levine2021} use it to explain stylised facts about pre-modern Europe, pre-modern India, the present-day United Kingdom and Spain, and 20th-century China --- my empirical results only test whether the theory can explain what happens in my dataset.

@@

Accounting for the possibility of attenuation bias from measurement error makes the null result look less unexpected and more like suggestive evidence.
